Figure 2 - Overview heatmaps for IP-MS and ChIP

### 2024-12-02 ms_figure_2_overview-heatmaps.Rmd
add facts-and-numbers to Figure 2 report
Co-authored-by: Merle Skribbe <merle.skribbe@gmail.com>
Co-authored-by: Charlotte Soneson <charlottesoneson@gmail.com>
Co-authored-by: Michael Stadler <stadler.michael@gmail.com>

>>>>

# Facts and numbers - ChIP-seq heatmap

```{r calc-numbers-heatmap, class.source="fold-show", warning=FALSE}
# percent of peaks in low H3 regions (log2 IP/input < 1.0)
usePeaks <- peakgr$peaktype != "common peaks (ubiquitous)"
cat(sprintf("Percent of binding sites in regions of low H3 ChIP-seq enrichment: %.1f %%\n",
            mean(chip_enr[usePeaks, "GSE108668_H3"] < 1.0) * 100))
cat(sprintf("Percent of binding sites in regions of high H3K14ac ChIP-seq enrichment: %.1f %%\n",
            mean(chip_enr[usePeaks, "GSE108668_H3K14ac"] >= 1.0) * 100))
```
